A Plot is Worth a Thousand Tests: Assessing Residual Diagnostics with the Lineup Protocol

### 2023-04-08 paper.tex
re-working section 2.2 and 5.1, 2.2 still needs more

Table \ref{tab:example-residual-plot-table} shows the RESET,
Breusch-Pagan and Shapiro-Wilk test results for the residual plots shown
in Figure \ref{fig:residual-plot-common-departures}. The RESET test and
Breusch-Pagan test were computed using the \texttt{resettest} and
\texttt{bptest} functions from R package \texttt{lmtest}, respectively.
The Shapiro-Wilk test was computed using the \texttt{shapiro.test} from
the core R package \texttt{stats}. (The the R package \texttt{skedastic}
\citep{skedastic} contains a large collection of tests for
heteroskedasticity.) The RESET test is exact, but the power parameter
must be chosen. \citet{ramsey_tests_1969} suggests using a power of
four, which is what we used. The Breusch-Pagan and Shapiro-Wilk tests
are approximate.

The Breusch-Pagan test and the Shapiro-Wilk test both reject \(H_0\) for
residual plots that display non-linearity and heteroscedasticity, even
though these are not the original intention of the test. As discussed in
\citet{cook1982residuals}, most residual-based tests for a particular
type of departure from model assumptions are also sensitive to other
types of departures. It is likely \(H_0\) is correctly rejected but for
the wrong reason, a phenomenon known as the ``Type III error''.
Additionally, outliers will often incorrectly trigger the rejection of
\(H_0\) despite when majority of the residuals are well-behaved
\citep{cook_applied_1999}. Furthermore, with a sufficiently large sample
size, residual-based tests may reject \(H_0\) due to a slight departure
that is of little practical significance. These can be largely avoided
in diagnostic plots as experienced analysts can evaluate the
acceptability of assumptions flexibly, even in the presence of outliers
and slight departures.

>>>>

Table \ref{tab:example-residual-plot-table} shows the RESET,
Breusch-Pagan and Shapiro-Wilk test results (\(p\)-values) for the
residual plots shown in Figure
\ref{fig:residual-plot-common-departures}. The RESET test and
Breusch-Pagan test were computed using the \texttt{resettest} and
\texttt{bptest} functions from R package \texttt{lmtest}, respectively.
The Shapiro-Wilk test was computed using the \texttt{shapiro.test} from
the core R package \texttt{stats}. (The the R package \texttt{skedastic}
\citep{skedastic} contains a large collection of tests for
heteroskedasticity.) The RESET test is exact, but the power parameter
must be chosen. \citet{ramsey_tests_1969} suggests using a power of
four, which is what we used. The Breusch-Pagan and Shapiro-Wilk tests
are approximate.

We would expect the RESET test for non-linearity to reject residual plot
B, the Breusch-Pagan test for heteroskedasticity to reject the residual
plot C, and Shapiro-Wilk test for non-normality to reject residual plot
D, which they all do and correctly fail to reject residual plot A.
Interestingly, the Breusch-Pagan and Shapiro-Wilk tests also reject the
residual plots exhibiting structure that they weren't designed for.
\citet{cook1982residuals} discusses that most residual-based tests for
particular types of departure from model assumptions are also sensitive
to other types of departures, that is, correctly rejected but for the
wrong reason, a phenomenon known as the ``Type III error''. Also, some
types of departure can also have elements of other types of departure,
for example, non-linearity could be viewed as heteroskedasticity.
Additionally, other problesms such as outliers can trigger the rejection
\citep{cook_applied_1999}. With a sufficiently large sample size,
residual-based tests may reject when there is only a slight departure.
This is a situation that is addressed by the results in this paper
because from a practical perspective we would only want to flag the
model as problematic when ther is a XXX diagnostic practical
significance. XXX check heteroscedastic spelling
